Sulfur Dioxide at Water's Surface

### 2011-02-22 EquilibratedOrientation.tex
Some changes to the SO2 equilibrated MD results (orientation), and added the two plots of density for the equilibrium MD.

\subsection{Water Orientation}

@@

Orientation distributions of the adsorbed \suldiox~molecules were created for both the neat-\wat~and saturated \suldiox~systems. Figure \ref{fig:so2-orientation} shows the distributions of $\cos(\theta)$ and $\cos(\phi)$ (arranged similar to the water orientation distributions in figure \ref{fig:water-orientation}). The data set for the neat-\wat~system is much smaller as only a single \suldiox~molecule was simulated. The resulting distribution plots are noisier than the corresponding saturated plots, but comparisons can still be drawn.

The location of \suldiox~within the water surface is slightly different between the two systems. The distribution of the single \suldiox~molecule is located just below the 0\angs position, and the distribution of the concentrated system is centered above the surface. This indicates that in both systems the \suldiox~is highly surface active, but the locations of the peak \suldiox~densities differ. The single molecule spends most of its time bound within the top water monolayer, and often traversing below that location by several\angs. The saturated system's surface molecules sit on top of the monolayer. The angular distribution of the single \suldiox~is concentrated primarily in $\cos(\theta)>0$ taking an orientation of the bisector pointing out of the water surface. This same distribution occurs in the saturated system for positions below 0\angs, but the orientation becomes isotropic for molecules located above 0\angs, on top of the water surface.

>>>>

\subsection{\wat~Orientation}

@@

Orientation distributions of the adsorbed \suldiox~molecules were created during the equilibrium simulations for both the neat-\wat~and saturated \suldiox~systems. Figure \ref{fig:so2-orientation} shows the distributions of $\cos(\theta)$ and $\cos(\phi)$ (arranged similar to the water orientation distributions plots in figure \ref{fig:water-orientation}). The data set for the neat-\wat~system is much smaller as only a single \suldiox~molecule was simulated in the bulk. The resulting distribution plots are thus noisier than the corresponding saturated plots, but effective comparisons can still be drawn.

The location of \suldiox~within the water surface is slightly different between the two equilibrium systems. The single \suldiox~molecule is generally located just below the 0\angs position of the surface, and the distribution of the concentrated system \suldiox~molecules is centered above the surface. This indicates that in both systems the \suldiox~is highly surface active, but the locations of the peak \suldiox~densities differ. The single molecule spends most of its time bound within the top water monolayer, and often traversing below that location by several\angs. The saturated system's surface molecules sit on top of the monolayer. The angular distribution of the single \suldiox~is concentrated primarily in $\cos(\theta)>0$ taking an orientation of the bisector pointing out of the water surface. This same distribution occurs in the saturated system for positions below 0\angs, but the orientation becomes isotropic for molecules located above 0\angs, on top of the water surface.
